Dismal Code: Studying the Evolution of Security Vulnerabilities

### 2013-02-03 docs/msr.tex
more content

First, we obtained the repository snapshot (January 2012) that was previously
used by -- et. al~\cite{}.

@@

>>>>

First, we obtained a snapshot (January 2012) of the maven repository and
handled it locally to retreive a list of all the names of the artifacts that existed in the
repository.

@@

Our experiment involved three entities: a Rabbit{\sc mq}
server,\footnote{\url{http://www.rabbitmq.com/}} a Python pool of worker
processes and a mongo{\sc db}.\footnote{\url{http://www.mongodb.org/}}
